\plaintitle

### 2017-06-16 papers/IoT2017/solution.tex
updates

In this section, we describe our solution for providing privacy to prosumers in a transactive energy IoT system, without compromising grid safety and security.
Figure~\ref{fig:softwareArchitecture} shows a high-level overview of the architecture of our solution.

\begin{figure}[h!]
\center
\begin{tikzpicture}[x=8cm, y=0.8cm, font=\small,
  nodeStyle/.style={rounded corners=0.1cm, drop shadow={shadow xshift=0.05cm, shadow yshift=-0.05cm, fill=black}}
]
%\draw [nodeStyle, fill=white]   (0, 0) rectangle    (1, 0.9) node [midway, align=center] {Communication network\\[-0.2em]and operating system};

@@

\draw [nodeStyle, fill=red!10] (0, 4.2) rectangle (0.49, 5.1) node [midway, align=center] {Anonymous trading\\[-0.2em]process for prosumers};
\draw [nodeStyle, fill=blue!10] (0.51, 4.2) rectangle (1, 5.1) node [midway, align=center] {Microgrid controller};
\end{tikzpicture}
\caption{High-level architecture of the proposed solution. Components marked red are introduced to provide privacy in a safe and secure manner. Components marked in blue are typical elements of a decentralized transactive microgrid.}
\label{fig:softwareArchitecture}
\end{figure}

@@

\draw[transfer] (smartmeter) -- node [asset, above] {\circled{1} energy\\production asset} (prosumer1);
\draw[transfer] (prosumer1) -- node [asset, above] {\circled{2} energy\\production asset} (mixing1);
\draw[transfer] (mixing1) -- node [asset, above] {\circled{3} energy\\production asset} (prosumer2);
\draw[transfer, dashed] (prosumer2) -- node [asset, above right, xshift=-1.5em, yshift=0.5em] {\circled{4} energy production asset,\\energy ask} (bidstorage);
\draw[transfer, dashed] (bidstorage) -- node [asset, below right] {energy\\ask} (partner);
\draw[transfer, bend right=30] (partner) to node [asset, below] {\circled{5} financial asset,\\energy consumption asset} (prosumer3);
\draw[transfer, bend right=50] (prosumer2) to node [asset, right, yshift=0.25em] {\circled{5} energy\\production asset} (partner);
\draw[transfer] (prosumer3) -- node [asset, below] {\circled{6} financial asset,\\
energy consumption asset} (smartmeter2);
\end{tikzpicture}
\caption{Simplified overview of the flow of assets from the perspective of a prosumer who sells energy. Note that in order to prevent de-anonymization, a prosumer should use multiple addresses and multiple rounds of mixing.}
\label{fig:sellFlow}
\end{figure*}

\subsection{Overview of the Trading Process}
We first provide a semi-formal description of the energy trading process from the prosumers' perspective.
In subsequent subsections, we will describe the assets, transactions, and services used for trading in more detail.

First, consider a prosumer who wishes to sell energy to another prosumer (this case is illustrated in Figure~\ref{fig:sellFlow}).
As its very first step, the prosumer withdraws an \emph{energy production asset} from its smart meter.
An energy production asset represents a permission to sell a certain amount of energy, and it is used to enforce safety requirements.
If the prosumer has sufficient unsold production capacity, the smart meter creates and transfers a production asset to the prosumer using a \emph{smart meter transaction} \circled{1}, which is recorded on the distributed ledger.

At this point, the production asset can still be traced back to the prosumer since the ledger is public.
To achieve anonymity, the prosumer uses a \emph{mixing service}, which in practice may be implemented as a decentralized protocol, such as CoinShuffle~\cite{ruffing2014coinshuffle} or Xim~\cite{bissias2014sybil}.
The prosumer transfers the production asset to the mixing service using an \emph{energy and financial transaction} \circled{2}, which is also recorded on the distributed ledger.
In turn, the mixing service transfers the production asset to an \emph{anonymous address} \circled{3}\Aron{We should probably insert a good definition here for readers who are unfamiliar with blockchain transactions.}, which is randomly generated and controlled by the prosumer.
Since the mixing service transfers assets from multiple prosumers to multiple anonymous addresses at the same time, and the anonymous addresses were generated at random by the prosumers, the assets cannot be traced back to the original prosumers after mixing.\footnote{Note that prosumers should divide their assets between multiple anonymous addresses; otherwise, each asset might be traced back to its prosumer based on the amount of energy that it contains.}

Now, the prosumer can engage in energy trading anonymously.
To find a trade partner, it can either post an \emph{energy ask} on the bid storage, or simply search the storage for an acceptable \emph{energy bid}.
To post an energy ask, the prosumer first proves to the storage service -- without revealing its original identity -- that it owns a production asset stored at an anonymous address.
It can then post the energy ask \circled{4}, which contains an anonymous communication identifier\footnote{We discuss communication anonymity later.}, a price, and a reference to the production asset.
If another prosumer, who would like to buy energy, finds the ask acceptable, it can contact the seller using the communication identifier given included in the ask.

@@

Finally, the selling prosumer deposits the financial and consumption assets to its smart meter using an energy and financial transaction.
To ensure that the prosumer remains anonymous, it transfers the assets to an anonymous address that is randomly generated and controlled by the smart meter \circled{6}.
Once the smart meter has received the assets, it credits the financial amount to and deducts the energy amount from the prosumer, for billing purposes.
In order to enforce safety requirements, the prosumer is required to always deposit the same amount of consumption assets as the amount of production assets withdrawn at the beginning; otherwise, unaccounted assets might be used to trade excessive amounts.

Second, consider a prosumer who would like to buy energy from another prosumer.
Since the trading process is very similar to the case of the selling prosumer, we will discuss only the differences.
In the first step, the prosumer tries to withdraw a financial asset and an energy consumption asset from its smart meter.
If the prosumer has the consumption capacity and good financial standing, the smart meter transfers the assets to the prosumer and adds the financial amount to the prosumer's bill.
After transferring the assets through a mixing service, the prosumer is ready to post an energy bid on the bid service.
To do so, it first proves the ownership of both the financial asset and the consumption asset to the service, and then posts the energy bid, which includes an anonymous communication identifier.
If a partner is found, the trade is executed as described before, the prosumer playing the role of the buyer this time.
Finally, the prosumer deposits the purchased energy production asset to the anonymous address of its smart meter,
which credits the energy amount to the prosumer, for billing purposes.
Note that if the prosumer has not spent all of its financial assets, then the remainder may also be deposited back to the smart meter.

>>>>

This section describes our solution for providing privacy to prosumers
in a transactive energy IoT system, without compromising grid safety
and security.
% Abhishek, could this figure appear earlier, i.e., in the previous
% section, as per my comment three?
Figure~\ref{fig:softwareArchitecture} shows the architecture of 
% Abhishek, can we give ``our solution'' a name so that we can refer
% to it by name throughout the paper?
our solution.  In this figure components marked red are introduced to
provide privacy in a safe and secure manner, whereas components marked
in blue are typical elements of a decentralized transactive microgrid.
\begin{figure}[h!]
\center
\begin{tikzpicture}[x=8cm, y=1.1cm, font=\small,
  nodeStyle/.style={rounded corners=0.1cm, drop shadow={shadow xshift=0.05cm, shadow yshift=-0.05cm, fill=black}}
]
%\draw [nodeStyle, fill=white]   (0, 0) rectangle    (1, 0.9) node [midway, align=center] {Communication network\\[-0.2em]and operating system};

@@

\draw [nodeStyle, fill=red!10] (0, 4.2) rectangle (0.49, 5.1) node [midway, align=center] {Anonymous trading\\[-0.2em]process for prosumers};
\draw [nodeStyle, fill=blue!10] (0.51, 4.2) rectangle (1, 5.1) node [midway, align=center] {Microgrid controller};
\end{tikzpicture}
\caption{High-level Architecture of Our Solution.}
\label{fig:softwareArchitecture}
\end{figure}

@@

\draw[transfer] (smartmeter) -- node [asset, above] {\circled{1} energy\\production asset} (prosumer1);
\draw[transfer] (prosumer1) -- node [asset, above] {\circled{2} energy\\production asset} (mixing1);
\draw[transfer] (mixing1) -- node [asset, above] {\circled{3} energy\\production asset} (prosumer2);
\draw[transfer, dashed] (prosumer2) -- node [asset, above right, xshift=-1.5em, yshift=0.5em] {\circled{4} energy production asset,\\energy ask} (bidstorage);
\draw[transfer, dashed] (bidstorage) -- node [asset, below right] {energy\\ask} (partner);
\draw[transfer, bend right=30] (partner) to node [asset, below] {\circled{5} financial asset,\\energy consumption asset} (prosumer3);
\draw[transfer, bend right=50] (prosumer2) to node [asset, right, yshift=0.25em] {\circled{5} energy\\production asset} (partner);
\draw[transfer] (prosumer3) -- node [asset, below] {\circled{6} financial asset,\\
energy consumption asset} (smartmeter2);
\end{tikzpicture}
\caption{Simplified Overview of the Flow of Assets from the Perspective of a Prosumer Who Sells Energy.}
\label{fig:sellFlow}
\end{figure*}

\subsection{Overview of the Trading Process}
We now provide a semi-formal description of the energy trading process
from the prosumers' perspective (subsequent subsections will describe
the assets, transactions, and services used for trading in more
detail).  Consider a prosumer who wishes to sell energy to another
prosumer, as shown in Figure~\ref{fig:sellFlow} In the initial step,
the prosumer withdraws an \emph{energy production asset} from its
smart meter.  An energy production asset represents a permission to
sell a certain amount of energy, and it is used to enforce safety
requirements.  If the prosumer has sufficient unsold production
capacity, the smart meter creates and transfers a production asset to
the prosumer using a \emph{smart meter transaction} \circled{1}, which
is recorded on the distributed ledger.

At this point, the production asset can still be traced back to the
prosumer since the ledger is public.  To achieve anonymity, the
prosumer uses a \emph{mixing service}, which could implemented as a
decentralized protocol, such as
CoinShuffle~\cite{ruffing2014coinshuffle} or
Xim~\cite{bissias2014sybil}. To prevent de-anonymization, a prosumer
should use multiple addresses and multiple rounds of mixing.

The prosumer next transfers the production asset to the mixing service
using an \emph{energy and financial transaction} \circled{2}, which is
also recorded on the distributed ledger.  In turn, the mixing service
transfers the production asset to an \emph{anonymous address},
\circled{3}
%\Aron{We should probably insert a good definition here for readers who are unfamiliar with blockchain transactions.}
which is randomly generated and controlled by the
prosumer.\footnote{The meaning of \emph{address} varies between
  distributed ledgers. Since our system could be implemented using any
  popular blockchain, such as Bitcoin and Ethereum, we use this term
  to denote a possible destination for asset transfers.  Assets that
  have been transferred to an address can be used only by someone who
  ``controls'' the address (typically, the one who generated it),
  which usually means knowing a private key that corresponds to the
  address.}
% knows the private key of the address (typically, the one who generated the address).}
Since the mixing service transfers assets from multiple prosumers to
multiple anonymous addresses at the same time---and the anonymous
addresses were generated at random by the prosumers---the assets
cannot be traced back to the original prosumers after
mixing.\footnote{prosumers should divide their assets between multiple
  anonymous addresses; otherwise, each asset might be traced back to
  its prosumer based on the amount of energy that it contains.}

A prosumer can now engage in energy trading anonymously.  To find a
trade partner, it can either post an \emph{energy ask} on the bid
storage, or simply search the storage for an acceptable \emph{energy
  bid}.  To post an energy ask, the prosumer first proves to the
storage service---without revealing its original identity---that it
owns a production asset stored at an anonymous address.  It can then
post the energy ask \circled{4}, which contains an anonymous
communication identifier (discussed shortly), a price, and a reference
to the production asset.  If another prosumer seeking to buy energy
finds the ask acceptable it can contact the seller using the
communication identifier included in the ask.

@@

The selling prosumer finally deposits the financial and consumption
assets to its smart meter using an energy and financial transaction.
to ensure that the prosumer remains anonymous, it transfers the assets
to an anonymous address that is randomly generated and controlled by
the smart meter \circled{6}.  Once the smart meter has received the
assets, it credits the financial amount to and deducts the energy
amount from the prosumer for billing purposes.  To enforce safety
requirements, the prosumer must always deposit the same amount of
consumption assets as the amount of production assets withdrawn at the
beginning since otherwise unaccounted assets might be used to trade
excessive amounts.

% Abhishek, it seems like we might need a transition here since the
% previous paragraph seemed to wrap up the ``Overview of the Trading
% Process'' subsection above.  It's not clear how the rest of this
% text ties in with that discussion.  Perhaps we could use
% subsubsections to make these parts more distinct? 
Consider a prosumer who wants to buy energy from another prosumer.
Since the trading process is similar to the case of the selling
prosumer, we only discuss the differences.  In the first step, the
prosumer tries to withdraw a financial asset and an energy consumption
asset from its smart meter.  If the prosumer has the consumption
capacity and good financial standing, the smart meter transfers the
assets to the prosumer and adds the financial amount to the prosumer's
bill.

After transferring the assets through a mixing service, the prosumer
is ready to post an energy bid on the bid service.  To do so, it first
proves the ownership of both the financial asset and the consumption
asset to the service, and then posts the energy bid, which includes an
anonymous communication identifier.  If a partner is found, the trade
is executed as described above, with the prosumer playing the role of
the buyer this time.

The prosumer finally deposits the purchased energy production asset to
the anonymous address of its smart meter, which credits the energy
amount to the prosumer, for billing purposes.  Note that if the
prosumer has not spent all of its financial assets, then the remainder
may also be deposited back to the smart meter.

### 2017-06-16 papers/IoT2017/transactions.tex
updates

In the previous subsection, we gave an overview of how transactions are used in the trading process to transfer various assets.
Here, we detail the format of these transactions, and the rules that they have to satisfy to be valid and recorded on the ledger.
We also introduce and detail the format of regulatory transactions, which the DSO uses to regulate the microgrid.

@@

\subsubsection{Assets}

Before we can discuss transactions, we must define the format of the three types of assets that these transactions may transfer.
First, an \emph{energy production asset} (EPA) is defined by
\begin{itemize}[noitemsep,topsep=-\parskip]
\item \field{power}: non-negative amount of power to produced (for example, measured in watts),
\item \field{start}: first time interval in which energy is to be produced,
\item \field{end}: last time interval in which energy is to be produced.
\end{itemize}
\vspace{\parskip}
Second, an \emph{energy consumption asset} (ECA) is defined by the same fields; however, for this asset, the fields define energy consumption instead of production.
Finally, a \emph{financial asset} (FA) is defined by a single non-negative number \field{amount}, which can be denominated in either a fiat currency (e.g., US dollars) or a cryptocurrency.

@@

Energy and financial transactions transfer energy and financial assets from one address to another.
Prosumers can use these transactions for multiple purposes: to trade energy by exchanging assets with other prosumers, to prove to the bid storage service that they possess an asset, to hide their identity by transferring assets to and from mixing services, and to deposit assets at their smart meter.
%
An energy and financial transaction contains the following fields:
\begin{itemize}[noitemsep,topsep=-\parskip]
\item \field{EPA\_in}: list of EPA inputs, each of which is defined by
\begin{itemize}[leftmargin=0.5em,nosep]
\item \field{out}: reference to an EPA output of a previous transaction,
\item \field{sig}: signature of the referenced output's address,
\end{itemize}
\item \field{ECA\_in}: list of ECA inputs, each of which is defined by
\begin{itemize}[leftmargin=0.5em,nosep]
\item \field{out}: reference to an ECA output of a previous transaction,
\item \field{sig}: signature of the referenced output's address,
\end{itemize}
\item \field{FA\_in}: list of FA inputs, each of which is defined by
\begin{itemize}[leftmargin=0.5em,nosep]
\item \field{out}: reference to an FA output of a previous transaction,
\item \field{sig}: signature of the referenced output's address,
\end{itemize}
\item \field{EPA\_out}: list of EPA outputs, each of which is defined by
\begin{itemize}[leftmargin=0.5em,nosep]
\item \field{EPA}: an energy production asset,
\item \field{address}: address to which EPA is transferred,
\end{itemize}
\item \field{ECA\_out}: list of ECA outputs, each of which is defined by
\begin{itemize}[leftmargin=0.5em,nosep]
\item \field{EPA}: an energy consumption asset,
\item \field{address}: address to which ECA is transferred,
\end{itemize}
\item \field{FA\_out}: list of FA outputs, each of which is defined by
\begin{itemize}[leftmargin=0.5em,nosep]
\item \field{EPA}: a financial asset,
\item \field{address}: address to which FA is transferred.
\end{itemize}
\end{itemize}
\vspace{0.5\parskip}
This transaction transfers the assets specified in the input lists to the addresses specified in the output lists. 
Input and output lists may differ in length, so one asset may be divided into multiple assets, and multiple assets may be combined into one.

An energy and financial transaction is valid (and can be recorded on the ledger) if the following three conditions hold.
\begin{itemize}[noitemsep,topsep=-\parskip]
\item None of the outputs referenced by the inputs have been spent by a transaction that has been recorded on the ledger.
\item All of the signatures are valid, which ensures that an asset can be transferred only by its current owner. % current owner can transfer an asset.
\item For each asset type (and for each timestep), the sums of the input and output assets are equal.
For example, in the case of energy production assets, the condition is
\begin{align*}
& \forall t: \sum_{\substack{out \,\in\, \field{EPA\_out}:\\out.\field{EPA}.\field{start} \leq t \leq out.\field{EPA}.\field{end}}} out.\field{EPA}.\field{power} \nonumber \\
& = \sum_{\substack{in \,\in\, \field{EPA\_in}:\\in.\field{out}.\field{EPA}.\field{start} \leq t \leq in.\field{out}.\field{EPA}.\field{end}}} in.\field{out}.\field{EPA}.\field{power}  .
%
%& \forall t: \sum_{out \in \field{EPA\_out}} out.\field{EPA}.\field{power} \cdot 1_{\left\{out.\field{EPA}.\field{start} \leq t \leq out.\field{EPA}.\field{end}\right\}} \nonumber \\
%& = \sum_{in \in \field{EPA\_in}} in.\field{out}.\field{EPA}.\field{power} \cdot 1_{\left\{in.\field{out}.\field{EPA}.\field{start} \leq t \leq in.\field{out}.\field{EPA}.\field{end}\right\}} ,
\end{align*}
%where $1_x$ is equal to $1$ if $x$ is true, and it is $0$ otherwise.
%\begin{equation}
%\forall t: \sum_{out \in \left\{out' \middle| out' \in \text{ EPA outputs} \wedge out'.EPA.start \leq t \leq out'.EPA.end\right\}} out.EPA.Power = \sum_{in \in \left\{in' \middle| in' \in \text{ EPA inputs} \wedge in'.EPA.start \leq t \leq in'.EPA.end\right\}} in.EPA.Power .
%\end{equation}
The conditions for consumption and financial assets can be described formally in similar ways.
\end{itemize}
%If a transaction submitted to the ledger is valid, it will be permanently recorded.

@@

The DSO uses regulatory transactions for two purposes: to manage the set of authorized smart meters and to change the price policy.
%First, to change the set of smart meters that are authorized to sign transactions, the DSO authorizes or bans individual smart meters.
First, whenever a new smart meter is installed, the DSO notifies the microgrid by authorizing the device using a regulatory transaction.
Similarly, whenever a smart meter is deactivated (e.g., because service is stopped or the device is believed to be faulty or compromised), the DSO notifies the microgrid by banning the device.
Second, to influence microgrid load, the DSO can set a price policy, which includes a price at which prosumer may buy energy from the DSO and a price at which they may sell energy to the DSO.

@@

A regulatory transaction of this type is valid if %the following two conditions hold:
%\begin{compactitem}
%\item 
\field{timestep} is not in the past and % specified in the transaction is in the future.
%\item 
the DSO's signature is valid.
%\end{compactitem}
%
The active prices for timestep $t$ are given by the last regulatory transaction recorded on the ledger whose \field{time} is less than $t$.
Similarly, regulatory transactions that are recorded on the ledger later override the authorizations and bans of earlier transactions.

>>>>

In the previous subsection, we gave an overview of how transactions
are used in the trading process to transfer various assets.  We now
describe the format of these transactions, as well as the rules that
they must satisfy to be valid and recorded on the ledger.  We also
introduce and detail the format of regulatory transactions, which the
DSO uses to regulate the microgrid.

@@

\subsubsection{Assets}
Before we discuss transactions, we'll define the format of the three
types of assets that these transactions may transfer.  First, an
\emph{energy production asset} (EPA) is defined by
\begin{itemize}[noitemsep,topsep=-\parskip]
\item \field{power}: non-negative amount of power to produced (for example, measured in watts),
\item \field{start}: first time interval in which energy is to be produced,
\item \field{end}: last time interval in which energy is to be produced.
\end{itemize}
\vspace{\parskip} Second, an \emph{energy consumption asset} (ECA) is
defined by the same fields.  For this asset, however, the fields
define energy consumption instead of production.  Finally, a
\emph{financial asset} (FA) is defined by a single non-negative number
\field{amount}, which can be denominated in either a fiat currency
(\em{e.g.}, Euros or US dollars) or a cryptocurrency (\em{e.g.},
Bitcoin or Ether).

@@

Energy and financial transactions transfer energy and financial assets
from one address to another.  Prosumers can use these transactions for
multiple purposes, {\em e.g.}, to trade energy by exchanging assets
with other prosumers, to prove to the bid storage service that they
possess an asset, to hide their identity by transferring assets to and
from mixing services, and to deposit assets at their smart meter.
%
An energy and financial transaction contains the following fields:
\begin{itemize}[noitemsep,topsep=-\parskip]
\item \field{EPA\_in}: list of EPA inputs, each of which is defined by
\begin{itemize}[leftmargin=0.5em,nosep]
\item \field{out}: reference to an EPA output of a previous transaction,
\item \field{sig}: signature of the referenced output's address,
\end{itemize}
\item \field{ECA\_in}: list of ECA inputs, each of which is defined by
\begin{itemize}[leftmargin=0.5em,nosep]
\item \field{out}: reference to an ECA output of a previous transaction,
\item \field{sig}: signature of the referenced output's address,
\end{itemize}
\item \field{FA\_in}: list of FA inputs, each of which is defined by
\begin{itemize}[leftmargin=0.5em,nosep]
\item \field{out}: reference to an FA output of a previous transaction,
\item \field{sig}: signature of the referenced output's address,
\end{itemize}
\item \field{EPA\_out}: list of EPA outputs, each of which is defined by
\begin{itemize}[leftmargin=0.5em,nosep]
\item \field{EPA}: an energy production asset,
\item \field{address}: address to which EPA is transferred,
\end{itemize}
\item \field{ECA\_out}: list of ECA outputs, each of which is defined by
\begin{itemize}[leftmargin=0.5em,nosep]
\item \field{EPA}: an energy consumption asset,
\item \field{address}: address to which ECA is transferred,
\end{itemize}
\item \field{FA\_out}: list of FA outputs, each of which is defined by
\begin{itemize}[leftmargin=0.5em,nosep]
\item \field{EPA}: a financial asset,
\item \field{address}: address to which FA is transferred.
\end{itemize}
\end{itemize}
\vspace{0.5\parskip} This transaction transfers the assets specified
in the input lists to the addresses specified in the output lists.
Input and output lists may differ in length, so one asset may be
divided into multiple assets, and multiple assets may be combined into
one.

An energy and financial transaction is valid (and can be recorded on
the ledger) if the following three conditions hold.
\begin{itemize}[noitemsep,topsep=-\parskip]
\item None of the outputs referenced by the inputs have been spent by
  a transaction that has been recorded on the ledger.
\item All the signatures are valid, which ensures that an asset can be
  transferred only by its current owner. 
% current owner can transfer an asset. 
\item For each asset type (and for each timestep), the sums of the
input and output assets are equal.  For example, in the case of
energy production assets, the condition is
\begin{align*}
& \forall t: \sum_{\substack{out \,\in\, \field{EPA\_out}:\\out.\field{EPA}.\field{start} \leq t \leq out.\field{EPA}.\field{end}}} out.\field{EPA}.\field{power} \nonumber \\
& = \sum_{\substack{in \,\in\, \field{EPA\_in}:\\in.\field{out}.\field{EPA}.\field{start} \leq t \leq in.\field{out}.\field{EPA}.\field{end}}} in.\field{out}.\field{EPA}.\field{power}  .
%
%& \forall t: \sum_{out \in \field{EPA\_out}} out.\field{EPA}.\field{power} \cdot 1_{\left\{out.\field{EPA}.\field{start} \leq t \leq out.\field{EPA}.\field{end}\right\}} \nonumber \\
%& = \sum_{in \in \field{EPA\_in}} in.\field{out}.\field{EPA}.\field{power} \cdot 1_{\left\{in.\field{out}.\field{EPA}.\field{start} \leq t \leq in.\field{out}.\field{EPA}.\field{end}\right\}} ,
\end{align*}
%where $1_x$ is equal to $1$ if $x$ is true, and it is $0$ otherwise.
%\begin{equation}
%\forall t: \sum_{out \in \left\{out' \middle| out' \in \text{ EPA outputs} \wedge out'.EPA.start \leq t \leq out'.EPA.end\right\}} out.EPA.Power = \sum_{in \in \left\{in' \middle| in' \in \text{ EPA inputs} \wedge in'.EPA.start \leq t \leq in'.EPA.end\right\}} in.EPA.Power .
%\end{equation}
The conditions for consumption and financial assets can be described
formally in similar ways.
\end{itemize}
%If a transaction submitted to the ledger is valid, it will be permanently recorded.

@@

The DSO uses regulatory transactions for two purposes: (1) to manage
the set of authorized smart meters and (2) to change the price policy.
%First, to change the set of smart meters that are authorized to sign transactions, the DSO authorizes or bans individual smart meters.
Whenever a new smart meter is installed, the DSO notifies the
microgrid by authorizing the device using a regulatory transaction.
Likewise, whenever a smart meter is deactivated (\em{e.g.}, because
service is stopped or the device is believed to be faulty or
compromised), the DSO notifies the microgrid by banning the device.
Second, to influence microgrid load, the DSO can set a price policy,
which includes a price at which prosumer may buy energy from the DSO
and a price at which they may sell energy to the DSO.

@@

A regulatory transaction of this type is valid if 
%the following two conditions hold:
%\begin{compactitem}
%\item 
\field{timestep} is not in the past and 
% specified in the transaction is in the future.
%\item 
the DSO's signature is valid.
%\end{compactitem}
%
The active prices for timestep $t$ are given by the last regulatory
transaction recorded on the ledger whose \field{time} is less than
$t$.  Likewise, regulatory transactions that are recorded on the
ledger later override the authorizations and bans of earlier
transactions.
